Supporting Information

### 2021-10-27 Asymptomatic_LSR_Supplement_noPrisma_yesROB_HI.Rmd
new update

rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")

@@

#Filtered by Q1
q1_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(quest___1 == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, `6` = rob_6)

@@

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(q3_sar == 1)  %>%
  select(authoryear, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = authoryear, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, `6` = rob_6)

>>>>

# rob_records$authoryear <- paste0(rob_records$author_1, " (", rob_records$year, ")")

@@

#Filtered by Q1
q1_rob <- df_rob %>%
  filter(!is.na(rob_1)) %>%
  filter(record_id != 122) %>%
  filter(quest___1 == 1)  %>%
  select(author_1, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6, record_id, quest___1, q3_sar, setting) %>%
  rename(Study = author_1, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, `6` = rob_6)

@@

###ROB analysis for Q2.1
q2_rob <- df_rob %>%
  filter(q3_sar == 1)  %>%
  select(author_1, rob_1, rob_2, rob_3, rob_4, rob_5, rob_6) %>%
  rename(Study = author_1, D1 = rob_1, D2 = rob_2, D3 = rob_3, D4 = rob_4,
         D5 = rob_5, `6` = rob_6)
